---
title: "project_draft"
output: html_document
---

Citation: Velloso, E.; Bulling, A.; Gellersen, H.; Ugulino, W.; Fuks, H. Qualitative Activity Recognition of Weight Lifting Exercises. Proceedings of 4th International Conference in Cooperation with SIGCHI (Augmented Human '13) . Stuttgart, Germany: ACM SIGCHI, 2013.

```{r, message=FALSE}
library(dplyr)
library(ggplot2)
library(GGally)
library(caret)
```

Import data:

```{r, cache=TRUE}
training <- read.csv("pml-training.csv")
```

Clean the data. First, let's get rid of variables we don't need:

```{r, cache=TRUE}
training <- training %>%
    select(-c(X, user_name, raw_timestamp_part_1, raw_timestamp_part_2,
              cvtd_timestamp, new_window, num_window))
```

We know all the remaining variables except `classe` are supposed to be numeric.

```{r, cache=TRUE}
training <- training %>%
    mutate_each(funs(suppressWarnings(as.numeric(as.character(.)))), -classe)
```

Use `ggpairs` to do some basic EDA.

```{r}
counter = seq(1, 30, by=3)
for (i in counter) {
    windows(20,10)
    training %>%
        select(classe, ) %>%
        ggpairs()
    }
```

Maybe just boxplots:

